
\begin{thebibliography}{9}


\addcontentsline{toc}{chapter}{Bibliografija}
{\small
\bibitem{andrews} Andrews G. E., ``\emph{The Geometric Series in Calculus}'', the American Mathematical Monthly, Vol. 105, Number 1, 1998.

\bibitem{barnett} Barnett S., ``\emph{Matrices - Methods and
Applications}'', Oxford applied mathematics and computing science
series, 1900.

\bibitem{chiang} Chiang A.C. , ``\emph{Osnovne metode ekonomije}'', MATE, Zagreb, 1994.
% Chiang, A. C.: Osnovne metode ekonomije, MATE, Zagreb, 1994.


\bibitem{demidovic} Demidovi\v{c} B. P., ``\emph{Zadaci i rije\v{s}eni primjeri iz vi\v{s}e matematike}'', Tehni\v{c}ka knjiga, Zagreb, 1978.

\bibitem{devlin} Devlin K., ``\emph{Sets, Functions and Logic}'',
Chapman \& Hall, 2004.

\bibitem{divjak:erjavec} Divjak B., Erjavec Z., ``\emph{Gospodarska i financijska
matematika}'', TIVA-FOI, Vara\v{z}din 2003.

\bibitem{divjak:hunjak} Divjak B., Hunjak T., ``\emph{Zbirka zadataka iz matematike}'', TIVA-FOI, 2003.

\bibitem{goodaire:parmenter} Goodaire, E. G., Parmenter, ``\emph{Discrete
Mathematics}'', Prentice Hall, Upper Saddle River, 2002.

\bibitem{hughes-hallett} Hughes-Hallett D., Gleason A. M. et al, ``\emph{Calculus}'', J. Wiley \& Sons Inc., 1994.

\bibitem{Hoffmann1} Hoffmann L. D., Bradley G. L., \textit{Finite
mathematics with Calculus}, McGraw-Hill, Inc. 1995.

\bibitem{horvatic} Horvati\'c K., ``\emph{Linearna Algebra I,
II}'', PMF, Zagreb, 1995.

%\bibitem{hortenson} Hortenson


\bibitem{mortensen} Mortensen M. E., ``\emph{Mathematics for Computer Graphics Applications}'', Industrial Press Inc., New York, 1999.

\bibitem{salas} Salas S., Hille E., Etgen G., ``\textit{Calculus: One and several
variables}'', J. Wiley, 1999.

\bibitem{simon} Simon C.P., Blume L., ``\emph{Mathematics for
Economists}'', W.W. Norton\& Co., New York, London 1994.

\bibitem{stanat:mcalister} Stanat D. R., McAllister D. F.,
``\emph{Discrete Mathematics in Computer Science}'', Prentice/Hall
International, 1977.

\bibitem{summers} Summers, J., ``\emph{Test your logic}: Fifty Puzzles in Deductive Reasoning'',
Dover Publications, 1972.

%\bibitem{silas} Silas?,

\bibitem{sikic:novovjekovna} \v{S}iki\'c, Z., ``\emph{Kako je stvarana novovjekovna matematika}'',
Školska Knjiga, Zagreb, 1989.

\bibitem{taylor:discrete} Ganier R., Taylor J., ``\emph{Discrete Mathematics for New Technology}'', Institute of Physics Publishing, Bristol, 1999.

\bibitem{veljan:starakombinatorika} Veljan, Darko,  ``\emph{Kombinatorika s teorijom grafova}'', \v{S}kolska knjiga, Zagreb, 1989.

\bibitem{vukovic} Vukovi\'c M., ``\emph{Matemati\v{c}ka logika I}'', PMF-MO, Zagreb, 2000.

}


\end{thebibliography}
